 

### 2022-02-24 doc/manuscript/tables_figures/schematic_summary.Rmd
some cleanup/organization
delete redundant figure
add asterisk /footnote to summary table
@camerondow35 , to your question on commit db49c84 (https://github.com/EcoClimLab/growth_phenology/commit/db49c843b14e8c195d5184124058358ef1bd91c9)

I added an example asterisk and footnote. Please modify both the table and footnote as appropriate.

![](schematic_v2.png)

@@

#add footnote: 
#kableExtra::footnote(number = c("'RP' and 'DP' refer to ring- and diffuse- porous species, respectively", "'-' and '+' = significant negative or positive response, respectively; 'n.s.'= no significant correlation"), footnote_as_chunk = FALSE, threeparttable=TRUE, escape = FALSE)
```

>>>>

![](schematic_summary.png)

@@

#add footnote: 
#kableExtra::footnote(number = c("'RP' and 'DP' refer to ring- and diffuse- porous species, respectively", "'-' and '+' = significant negative or positive response, respectively; 'n.s.'= no significant correlation"), footnote_as_chunk = FALSE, threeparttable=TRUE, escape = FALSE)
```
*not biologically significant
